### 2023-04-12 output/group_0_crimes_500m/tables/pre_treatment_covariate_tests.tex
generated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.53 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.34 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.34 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.06 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
 & Filing without cause & 0.02 & 0.16 \\
 & Filing for nonpayment & 0.00 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.25 & 0.00 \\
 & Plaintiff has attorney & 0.38 & 0.06 \\
 & Defendant is entity & 0.00 & 0.13 \\
 & Plaintiff is entity & 0.02 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.54 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.40 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.09 & 0.65 \\
 & Job density, 2013 & 0.00 & 0.97 \\
 & Median household income, 2016 & 0.68 & 0.07 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.65 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.41 & 0.01 \\
 & Filing without cause & 0.01 & 0.02 \\
 & Filing for nonpayment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.00 \\
 & Plaintiff has attorney & 0.63 & 0.00 \\
 & Defendant is entity & 0.00 & 0.09 \\
 & Plaintiff is entity & 0.03 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
generated figures

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.88 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.60 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.44 & 0.07 \\
 & Job density, 2013 & 0.00 & 0.15 \\
 & Median household income, 2016 & 0.56 & 0.03 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.80 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.05 & 0.01 \\
 & Filing without cause & 0.08 & 0.59 \\
 & Filing for nonpayment & 0.01 & 0.02 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.77 & 0.04 \\
 & Plaintiff has attorney & 0.84 & 0.19 \\
 & Defendant is entity & 0.00 & 0.07 \\
 & Plaintiff is entity & 0.26 & 0.03 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.55 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.93 \\
 & Job density, 2013 & 0.00 & 0.73 \\
 & Median household income, 2016 & 0.00 & 0.11 \\
 & Poverty rate, 2010 & 0.69 & 0.66 \\
 & Population density, 2010 & 0.00 & 0.23 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.48 & 0.00 \\
 & Filing without cause & 0.05 & 0.00 \\
 & Filing for nonpayment & 0.00 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.02 & 0.00 \\
 & Plaintiff has attorney & 0.92 & 0.00 \\
 & Defendant is entity & 0.14 & 0.00 \\
 & Plaintiff is entity & 0.51 & 0.01 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-12 output/summary_statistics/tables/summary_statistics.tex
generated figures

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -164.98 & 222.44 & 3,171 \\
 & Total Crime Incidents, 2017 & 1,230.16 & 697.53 & 3,171 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.30 & 0.21 & 3,171 \\
 & Job density, 2013 & 15,603.89 & 41,982.90 & 3,171 \\
 & Median household income, 2016 & 46,085.28 & 24,946.22 & 3,171 \\
 & Poverty rate, 2010 & 0.29 & 0.15 & 3,171 \\
 & Population density, 2010 & 23,385.01 & 13,324.90 & 3,171 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.36 & 3,171 \\
 & Filing without cause & 0.05 & 0.23 & 3,171 \\
 & Filing for nonpayment & 0.79 & 0.41 & 3,171 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.04 & 0.20 & 3,171 \\
 & Plaintiff has attorney & 0.87 & 0.34 & 3,171 \\
 & Defendant is entity & 0.02 & 0.13 & 3,171 \\
 & Plaintiff is entity & 0.82 & 0.39 & 3,171 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 22.33 & 23.38 & 3,039 \\
 & Judgment by default & 0.25 & 0.43 & 3,171 \\
 & Case dismissed & 0.20 & 0.40 & 3,171 \\
 & Case heard & 0.02 & 0.14 & 3,171 \\
 & Money judgment & 1,806.43 & 4,135.66 & 3,171 \\
 & Case mediated & 0.48 & 0.50 & 3,171 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Change in Crime Incidents, 2017-2019 & -152.00 & 217.38 & 1,632 \\
 & Total Crime Incidents, 2017 & 1,162.73 & 714.55 & 1,632 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.31 & 0.22 & 1,632 \\
 & Job density, 2013 & 16,511.95 & 43,184.21 & 1,632 \\
 & Median household income, 2016 & 46,399.34 & 25,059.82 & 1,632 \\
 & Poverty rate, 2010 & 0.29 & 0.15 & 1,632 \\
 & Population density, 2010 & 23,373.29 & 14,260.04 & 1,632 \\
\cline{1-5}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.32 & 1,632 \\
 & Filing without cause & 0.04 & 0.20 & 1,632 \\
 & Filing for nonpayment & 0.76 & 0.43 & 1,632 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.03 & 0.18 & 1,632 \\
 & Plaintiff has attorney & 0.91 & 0.29 & 1,632 \\
 & Defendant is entity & 0.02 & 0.15 & 1,632 \\
 & Plaintiff is entity & 0.84 & 0.36 & 1,632 \\
\cline{1-5}
\multirow[c]{10}{4cm}{\textit{Panel E: Case Resolution}} & Case duration & 19.82 & 24.51 & 1,538 \\
 & Judgment by default & 0.48 & 0.50 & 1,632 \\
 & Case dismissed & 0.41 & 0.49 & 1,632 \\
 & Case heard & 0.05 & 0.21 & 1,632 \\
 & Execution issued & 0.30 & 0.46 & 1,632 \\
 & Money judgment & 1,456.98 & 3,445.07 & 1,632 \\
 & Execution levied & 0.06 & 0.23 & 1,632 \\
 & Case mediated & 0.00 & 0.00 & 1,632 \\
 & Execution requested & 0.02 & 0.15 & 1,632 \\
 & Execution status unknown & 0.00 & 0.00 & 1,632 \\
\cline{1-5}
\bottomrule
\end{tabular}
